% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yang Shuoliu}

\basicInfo{
  \email{visysl@outlook.com} \textperiodcentered\ 
  \phone{(+86) 155-571-80427} \textperiodcentered}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Zhejiang University}, HangZhou, China}{2017 -- 2020}
\textit{Master student} in College of Computer Science and Technology (CS)
\datedsubsection{\textbf{Centrol South University}, ChangSha, China}{2013 -- 2017}
\textit{B.S.} in School of Aeronautic and Astronautics (AA)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Netease (Hangzhou) Corp.} HangZhou, China}{2020.4 -- Present}
\role{Game Client Developer}{}
\begin{itemize}
  \item User Interface Development
  \subsection{Involves game data display, visual representation and essential interaction logic for player in client.}

  \item Special Effects and Post-Processing by GPU Shader Programming
  \subsection{Applies procedural shading and post-processing to make visual effects more efficient comparing with traditional ways.}

  \item Developing and Maintaining of Toolchains
  \subsection{Optimizes the localization tool and plugin of game assets management to improve their perfermance.}

\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Python, Rust, C\#, CUDA etc.
  \item Know the concept of computer graphics and rendering.
  \item Essential Qt GUI (QtWidget) framework experience.
  \item Basic experience on Unity3D game engine.
  \item Know the concept of operating system.
\end{itemize}

\section{\faUsers\ Projects}

\begin{itemize}

\item \textbf{Vulkan Tutorial} (\url{https://space.bilibili.com/12690590/channel/detail?cid=180474})

\begin{itemize}
  \item A video tutorial for vulkan beginners. These video are organized in coding step by step.
\end{itemize}


\item \textbf{Large Volume Data Renderer} (\url{https://github.com/cad420/VolumeVisualizationGL})

\begin{itemize}
  \item 
  \subsection{My undergraduate project for large volume data rendering. It can render serveral 
  tera-bytes volume data in an acceptable FPS in a way of combining GPU-driven method and data compression.}
\end{itemize}


\item \textbf{VM-serial library} (\url{https://github.com/cad420/VMCore}, \url{https://github.com/cad420/VMat},\\ 
 \url{https://github.com/cad420/VMUtils})

\begin{itemize}
\item Personal use libraries for basic C++ development. These simple and light-weight infrastructures make
 me handy to develop in C++. Smart pointer, plugin framework and memory management, logger etc. are included.
\end{itemize}

\item \textbf{EMExplore} (\url{https://github.com/yslib/EMExplorer})

\subsection{An editor provides a workflow to view assisted with image processing and render data generated by scanning electron microscope. 
It supports marking by a pen tool and building it into mesh and management of these stuff.}

\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Technical Blog: \url{http://visysl.com}
  \item GitHub: \url{https://github.com/yslib}
\end{itemize}


\end{document}
